\begin{thebibliography}{10}

\bibitem{DBLP:conf/sigir/AlonsoS18}
O.~Alonso and T.~Sellam.
\newblock Quantitative information extraction from social data.
\newblock SIGIR 2018.

\bibitem{DBLP:series/irs/Balog18}
K.~Balog.
\newblock {\em Entity-Oriented Search}.
\newblock {\em The Information
  Retrieval Series}, Springer, 2018.

\bibitem{DBLP:journals/ftir/BastBH16}
H.~Bast, B.~Buchhold, and E.~Haussmann.
\newblock Semantic search on text and knowledge bases.
\newblock {\em Foundations and Trends in Information Retrieval}, 2016.

\bibitem{DBLP:conf/rweb/BastS18}
H.~Bast and N.~Schnelle.
\newblock Efficient and convenient sparql+text search: {A} quick survey.
\newblock Reasoning Web 2018.

\bibitem{DBLP:conf/acl/GardnerC18}
C.~Clark and M.~Gardner.
\newblock Simple and effective multi-paragraph reading comprehension.
\newblock ACL 2018.

\bibitem{DBLP:journals/kais/DiefenbachLSM18}
D.~Diefenbach et al.
\newblock Core techniques of question answering systems over knowledge bases: a
  survey.
\newblock {\em Knowl. Inf. Syst.}, 2018.

\bibitem{DBLP:conf/ecir/GarigliottiB18}
D.~Garigliotti and K.~Balog.
\newblock Towards an understanding of entity-oriented search intents.
\newblock ECIR 2018.

\bibitem{DBLP:conf/acl/HeLLZ17a}
L.~He et al.
\newblock Deep semantic role labeling: What works and what's next.
\newblock ACL 2017.

\bibitem{HoISWC2019}
V.~T. Ho, Y.~Ibrahim, K.~Pal, K.~Berberich, and G.~Weikum.
\newblock Qsearch: Answering quantity queries from text.
\newblock ISWC 2019.

\bibitem{DBLP:conf/sigir/HoffartMW14}
J.~Hoffart, D.~Milchevski, and G.~Weikum.
\newblock {STICS:} searching with strings, things, and cats.
\newblock SIGIR 2014.

\bibitem{DBLP:conf/emnlp/HoffartYBFPSTTW11}
J.~Hoffart et al.
\newblock Robust disambiguation of named entities in text.
\newblock EMNLP 2011.

\bibitem{DBLP:conf/wsdm/HuangZLL19}
X.~Huang et al.
\newblock Knowledge graph embedding based question answering.
\newblock WSDM 2019.

\bibitem{DBLP:conf/cikm/IbrahimRW16}
Y.~Ibrahim, M.~Riedewald, and G.~Weikum.
\newblock Making sense of entities and quantities in web tables.
\newblock CIKM 2016.

\bibitem{DBLP:journals/cacm/NoyGJNPT19}
N.~F. Noy et al.
\newblock Industry-scale knowledge graphs: lessons and challenges.
\newblock {\em Commun. {ACM}}, 2019.

\bibitem{DBLP:conf/emnlp/PenningtonSM14}
J.~Pennington, R.~Socher, and C.~D. Manning.
\newblock Glove: Global vectors for word representation.
\newblock EMNLP 2014.

\bibitem{DBLP:conf/emnlp/RajpurkarZLL16}
P.~Rajpurkar et al.
\newblock Squad: 100, 000+ questions for machine comprehension of text.
\newblock EMNLP 2016.

\bibitem{DBLP:journals/tacl/RoyVR15}
S.~Roy, T.~Vieira, and D.~Roth.
\newblock Reasoning about quantities in natural language.
\newblock {\em {TACL}} 2015.

\bibitem{DBLP:conf/acl/SahaPM17}
S.~Saha, H.~Pal, and Mausam.
\newblock Bootstrapping for numerical open {IE}.
\newblock ACL 2017.

\bibitem{DBLP:conf/kdd/SarawagiC14}
S.~Sarawagi and S.~Chakrabarti.
\newblock Open-domain quantity queries on web tables: annotation, response, and
  consensus models.
\newblock KDD 2014.

\bibitem{DBLP:conf/www/SuchanekKW07}
F.~M. Suchanek, G.~Kasneci, and G.~Weikum.
\newblock Yago: a core of semantic knowledge.
\newblock WWW 2007.

\bibitem{ZhangBalog:TOIT2020}
S. Zhang and K. Balog.
\newblock Web Table Extraction, Retrieval and Augmentation: A Survey.
\newblock TOIT 11(2), 2020.
 


\end{thebibliography}

